Models

### 2023-10-03 analysis/models.qmd
logistic

@@

# convert mrs to ordered factors
mrs_levels <- c("0", "1", "2", "3", "4", "5", "6")

data <- data |>
  mutate(
    mrs_30 = fct_inseq(as.character(mrs_30), ordered = TRUE),
    mrs_90 = fct_inseq(as.character(mrs_90), ordered = TRUE),
    mrs_180 = fct_inseq(as.character(mrs_180), ordered = TRUE),
    mrs_270 = fct_inseq(as.character(mrs_270), ordered = TRUE),
    mrs_365 = fct_inseq(as.character(mrs_365), ordered = TRUE),
  ) |>
  filter(ich_location == "Basal Ganglia" | ich_location == "Thalamus" | ich_location == "Lobar")

@@

tidy(fit_brms) |>
  select(c(estimate, conf.low, conf.high))

@@

plot_predictions(fit_brms, condition = c("ich_location", "ich_laterality"), type = "prediction")

>>>>

data <- data |>
  filter(ich_location == "Basal Ganglia" | ich_location == "Thalamus" | ich_location == "Lobar")

@@

@@

@@
